Verifying Demonstrations

### 2017-09-27 SystemModel.tex
Writes up system model, moves adversary model to properties

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
  \(id\in \Z_{2^\lambda}\) is an identifier,
  \((t_s, t_e)\in \R^2\) is a time interval,
  \((x, y)\in \R^2\) are the coordinates of the location.
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

\mode<presentation>{%
\begin{frame}
\begin{definition}[Protest]
  \begin{itemize}
    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
    \item \(id\in \Z_{2^\lambda}\) is an identifier,
    \item \((t_s, t_e)\in \R^2\) is a time interval,
    \item \((x, y)\in \R^2\) are the coordinates of the location.
    \item A \emph{protest} is a set of subprotests sharing the same \(id\).
  \end{itemize}
\end{definition}
\end{frame}
}

@@

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ contain its \(id\).
Furthermore it must provide the time and the location of the participation.
More formally, we define a participation proof as follows.

\begin{definition}[Participation proof]
  A \emph{witness signature}\footnote{%
    \Iac{LPS}?
  }is a tuple \[(pid; id; t_s, t_e; x, y; \sigma),\] where
  \(pid\) is a protester's identity,
  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest} and
  \(\sigma\) is a signature over the values in the tuple.
  A \emph{participation proof} \[P_{i, j} = \{ (pid; id; t_s, t_e; x, y; \sigma) 
    \mid pid = i, id = j\}\] for a protester \(i\) participating in protest 
  \(j\) is the set of all witness signatures with the same protester and protest 
  identifiers.
\end{definition}

\mode<presentation>{%
  \begin{frame}
    \begin{definition}[Participation proof]
      \begin{itemize}
        \item A \emph{witness signature} is a tuple \((pid; id; t_s, t_e; x, y; 
            \sigma)\), where
        \item \(pid\) is a protester's identity,
        \item \(id, t_s, t_e, x, y\) are as before,
        \item \(\sigma\) is a signature over the values.
        \item A \emph{participation proof} \(P_{i, j} = \{ (pid; id; t_s, t_e; x, 
            y; \sigma) \mid pid = i, id = j\}\).
      \end{itemize}
    \end{definition}
  \end{frame}
}

\subsection{Adversary model}

We have three adversaries: Alice herself, Eve and Rusuk.
Alice the protest organizer tries to increase the count.
Eve the totalitarian dictator tries to decrease the count.
Additionally, Eve tries to deanonymize the participants.
Finally, we have Rusuk who is the head of another nation state.
Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
gain, thus supporting either Eve or Alice.
Rusuk will thus also try to either increase or decrease the count.

\mode<presentation>{%
\begin{frame}
  \begin{block}{Alice the activist}
    \begin{itemize}
      \item Alice organizes the protest against Eve's regime.
      \item Alice wants to have a high participation count.
      \item She tries to increase it.
    \end{itemize}
  \end{block}

  \begin{block}{Eve the fake-news populist}
    \begin{itemize}
      \item Eve's regime is target of the protest.
      \item She wants to have a low participation count.
      \item She tries to decrease it.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Eve the totalitarian dictator}
    \begin{itemize}
      \item Eve wants to \enquote{convince} activists to support her.
      \item She wants to find all activists.
      \item She tries to identify (deanonymize) participants.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Rusuk the nation state}
    \begin{itemize}
      \item Rusuk benefits from the situation in Evestan.
      \item He wants the outcome to be the most beneficial.
      \item He will try to increase or decrease the participation count.
    \end{itemize}
  \end{block}
\end{frame}
}

More formally \dots

\mode<all>\endinput

\section{Old stuff}

We can divide the problem into three parts:
\begin{itemize}
  \item Register participants in the system.
  \item Collect the necessary data.
  \item Perform the counting and verification.
\end{itemize}

To register the participants we might be able to piggy-back on existing 
\acp{PKI} and blind signatures --- similarly as for voting systems.

There are several issues that must be treated:
\begin{itemize}
  \item Each location proof must be bound to one individual's participation.
    One protester must not be able to create two unique location proofs and be 
    able to increase the number of participants, that would violate 
    \cref{EligibilityVerif} above.
    In other words, we must prevent the Sybil attack.

  \item A group of people should not be able to generate \acp{LP} to make it 
    look as if they participated in the protest but actually stayed at home.
    This means that all \acp{LP} must be linked to each other.
    If a protest has hundreds of thousands of participants, then this linking 
    must be achieved efficiently.
\end{itemize}

The model will be a public anonymous blackboard.
We will use this blackboard to publish locations proofs after the protest.

We want the following properties:
\begin{description}
  \item[Correctness] We want to count everyone once and only once.
  \item[Unforgeability] Participation should not be possible to forge.
    I.e.\ non-participants should not be able to say they were present.
    This together with correctness will provide authenticity to the protest 
    verification.
  \item[Anonymity] Given the data published on the blackboard, the adversary 
    should not be able to tell two participants apart.
  \item[Decentralized] There should be no central authority.
\end{description}

Can the adversary publish a public-key looking random string to sabotage the 
blackboard?

Basically the properties that we are interested in are similar to those of 
electronic voting, so we would like to reuse as many definitions from there as 
possible.

\subsection{Decentralization}

In \ac{PROPS} the prover must have a secret signed by \iac{CA}.
This \ac{CA} can be implemented as a secret-sharing scheme.
Usually these have a fixed threshold \((t, n)\).
This can be achieved by commitments, then the shared secret is computed.
However, it would be interesting to have the threshold dynamically adapt to the 
number of participants, i.e.\ participants can join later too.

Can the adversary then \enquote{join} enough many to throw off the threshold?

\subsection{Correctness and Unforgeability}

Each prover must reach a threshold of witnesses \(k\).
We must be able to prevent a prover to collect \(2k\) witnesses and then 
publishing two proofs.
We therefore must achieve conditional linkability between the \acp{LP} 
published on the blackboard.
If a second \ac{LP} for a secret is published, then those should be linkable.
This might be possible to achieve with unique group 
signatures~\cite{UniqueGroupSignatures,UniqueRingSignatures,ListSignatures}.

>>>>

\begin{frame}
\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((id, t, l)\) where
  \(id\in \Z_{2^\lambda}\) is an identifier,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}
\end{frame}

@@

\subsection{Participation and count}

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its \(id\), time and 
location.
We use witnesses to associate the proof to the location.
The proof and its witnesses are stored in a set, as there should be only unique 
witnesses.

\begin{frame}
\begin{definition}[Witness]
  A \emph{witness} \(w = (pid, id, t, l, wid)\) is a tuple where
  \(id, t, l\) are as in \cref{DefProtest},
  \(pid\) uniquely identifies the protester and \(wid\) uniquely identifies the 
  person who issued the witness.
  We let \(W\) be the set of all witnesses.
\end{definition}
\end{frame}

A subset of the witnesses forms a participation proof for a protester.

\begin{frame}
\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{align}
    \nonumber
    p_{i, j} =
    \left\{ (pid, id, t, l, wid)\in W \mid
    %\right. &
    pid = i, id = j,
    %\\ & \left.
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{align}
  of all witnesses with the same protester and protest identifiers, witness time 
  interval \(t\) and location \(l\) is within those of the protest \(j\) (i.e.\ 
  \(t_j\) and \(l_j\)).
\end{definition}
\end{frame}

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(id\) as the 
  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
      j = id, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \interval{0}{1}\) and 
  a threshold \(\theta\).
\end{definition}

### 2017-09-27 properties.tex
Writes up system model, moves adversary model to properties

\mode*
\section{Desired properties}%
\label{Properties}

We categorize the desired properties into verifiability and privacy.

\subsection{Verification}%
\label{Verification}

>>>>

\mode*
\section{Desired security properties}%
\label{Properties}

%\subsection{An overview of the adversary}

We have three \emph{malicious} adversaries: Alice, Eve and Rusuk.
Alice the activist (and all the protesters) try to increase the count.
Eve the totalitarian dictator tries to decrease the count.
Additionally, Eve tries to deanonymize the participants to arrest them or 
\enquote{convince} them to change their minds.
Finally, we have Rusuk who is represents another nation state.
Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
gain, thus supporting either Eve or Alice as he see fits.
Rusuk will thus also try to either increase or decrease the count.
We will now formally define some security properties specifying the 
computational effort needed by the adversaries to succeed.
We categorize the desired properties into verifiability and privacy.

\mode<presentation>{%
\begin{frame}
  \begin{block}{Alice the activist}
    \begin{itemize}
      \item Alice organizes the protest against Eve's regime.
      \item Alice wants to have a high participation count.
      \item She tries to increase it.
      \item So does \emph{all the protesters}.
    \end{itemize}
  \end{block}

  \pause{}

  \begin{block}{Eve the fake-news populist}
    \begin{itemize}
      \item Eve's regime is target of the protest.
      \item She wants to have a low participation count.
      \item She tries to decrease it.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Eve the totalitarian dictator}
    \begin{itemize}
      \item Eve wants to \enquote{convince} activists to support her.
      \item She wants to find all activists.
      \item She tries to identify (deanonymize) participants.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Rusuk the nation state}
    \begin{itemize}
      \item Rusuk benefits from the situation in Evestan.
      \item He wants the outcome to be the most beneficial.
      \item He will try to increase or decrease the participation count.
    \end{itemize}
  \end{block}
\end{frame}
}

\subsection{Verifiability}%
\label{Verifiability}
